Prefetching SPARQL query cacher

### 2016-07-28 dissertation/cache-proxy.tex
use same prefix

The implementation consists of several modules that have been
published to the Comprehensive Perl Archive Network as Free Software,
and most of which have become a part the Free Software ecosystem. For
a detailed account of the modules that are a part of the system and
the authors that have contributed code in this ecosystem, see
Appendix~\ref{app:modules}. Some parts are essential for the
discussion and to understand the contributions, and therefore detailed
in the following:

@@

In addition to caching the prefetched results, the proxy may also
cache the serialized results of any full SPARQL query, and also enter
the results of any Linked Data Fragment retrieved when the query
planner evaluates a query into the above cache, using a trivial
extension to the plan class in Section~\ref{sec:ldfclient}.

@@

These query planners are a good example of the virtues of traits-based
programming, as they are typically customised along different axes:
access plans, cost estimation, planning of joins within Basic Graph
Patterns or left joins, rewriting (like gathering quad patterns to
blocks), etc. In the case of our query planner that combines a remote
endpoint with a local cache, named
\pmodule{AtteanX::QueryPlanner::Cache}, the basic query planner of the
Attean framework, \pmodule{Attean::QueryPlanner} is extended
(i.e. inherited from), but also composes the following roles:
\pmodule{Attean::API::NaiveJoinPlanner},
\pmodule{Attean::API::SimpleCostPlanner},
\pmodule{AtteanX::API::JoinRotatingPlanner},
\pmodule{AtteanX::Query::AccessPlan::SingleQuadBGP} and
\pmodule{AtteanX::Query::AccessPlan::Cache}, out of which the three
first are a part of the Attean framework, the next was described in
Section~\ref{sec:sparqlclient} and the last is a part of the
query cache system itself.

@@

%\section{Appendix}
\section{Appendix: Modules and Their Contributors}\label{app:modules}

>>>>

The implementation consists of several modules that have been
published to the Comprehensive Perl Archive Network as Free Software,
and most of which have become a part the Free Software ecosystem. For
a detailed account of the modules that are a part of the system and
the authors that have contributed code in this ecosystem, see
Appendix~\ref{sec:modules}. Some parts are essential for the
discussion and to understand the contributions, and therefore detailed
in the following:

@@

In addition to caching the prefetched results, the proxy may also
cache the serialized results of any full SPARQL query, and also enter
the results of any Linked Data Fragment retrieved when the query
planner evaluates a query into the above cache, using a trivial
extension to the plan class packaged with the LDF client code
described in Appendix~\ref{sec:ldfclient}.

@@

These query planners are a good example of the virtues of traits-based
programming, as they are typically customised along different axes:
access plans, cost estimation, planning of joins within Basic Graph
Patterns or left joins, rewriting (like gathering quad patterns to
blocks), etc. In the case of our query planner that combines a remote
endpoint with a local cache, named
\pmodule{AtteanX::QueryPlanner::Cache}, the basic query planner of the
Attean framework, \pmodule{Attean::QueryPlanner} is extended
(i.e. inherited from), but also composes the following roles:
\pmodule{Attean::API::NaiveJoinPlanner},
\pmodule{Attean::API::SimpleCostPlanner},
\pmodule{AtteanX::API::JoinRotatingPlanner},
\pmodule{AtteanX::Query::AccessPlan::SingleQuadBGP} and
\pmodule{AtteanX::Query::AccessPlan::Cache}, out of which the three
first are a part of the Attean framework, the next is described in
Appendix~\ref{sec:sparqlclient} and the last is a part of the
query cache system itself.

@@

%\section{Appendix}
\section{Appendix: Modules and Their Contributors}\label{sec:modules}
